\textls[-15]{\thetitle \mbox{(Technical Report)}}

### 2022-11-04 cc-condensed.tex
Add one sentence for metatheory.
edit

\noindent
Consistency says that the type $\bot$ is not inhabited.
Thus, it is safe to use the type theory for logical reasoning, as not
every proposition is trivially provable.
\cref{thm:consistency} is a consequence of a meta\-circular interpretation of all
the well-formedness rules, which, in particular, interprets $\bot$ in
\TT as an uninhabited type in the meta\-language.
The construction of this interpretation follows the standard model of
\citet{altkap2016}, extending it to handle linkages.
We refer the reader to a supplemental file (in Agda syntax) for the complete proof.

@@

We prove \cref{thm:canonicity} by constructing a logical-relations model
for the well-formedness rules, following prior approaches~\cite{coquand2018canonicity,sterling2019algebraic,kaposi2019gluing}.
In particular, a closed, well formed type $\goodType{\cdot}{T}{}$ is interpreted
as a logical predicate on closed terms: the predicate includes all
closed, reducible terms of type~$T$.
The proof is available as a supplemental file in Agda syntax.

>>>>

\noindent
Consistency says that the type $\bot$ is not inhabited.
Thus, it is safe to use the type theory for logical reasoning, as not
every proposition is trivially provable.
\cref{thm:consistency} is a consequence of a meta\-circular interpretation of all
the well-formedness rules, which, in particular, interprets $\bot$ in
\TT as an uninhabited type in the meta\-language.
The construction of this interpretation follows the standard model of
\citet{altkap2016}, extending it to handle linkages.
Linkages~$\LkgAdd{\lkg}{t}$ can be interpreted into non-dependent products,
as rule \ruleref{l/add} indicates.
%
We refer the reader to a supplemental file (in Agda syntax) for the complete proof.

@@

We prove \cref{thm:canonicity} by constructing a logical-relations model
for the well-formedness rules, following prior approaches~\cite{coquand2018canonicity,sterling2019algebraic,kaposi2019gluing}.
In particular, a closed, well formed type $\goodType{\cdot}{T}{}$ is interpreted
into a logical predicate on closed terms: the predicate includes all
closed, reducible terms of type~$T$.
The proof is available as a supplemental file in Agda syntax.
